Union and intersection contracts are hard, actually

### 2021-06-10 paper.tex
Set US English dictionary in Emacs
Remove reference to flat contracts
User-defined contracts are a subset of flat contracts but these are not
the same thing. Flat contracts is basically non-composed contracts (base
types + user-defined).
Section 5: moving Section 4.3 in + subsection titles
*Multiple* inheritance

Yet, intersections are useful in their own right. They can be used to
combine dictionaries in the style of object-oriented inheritance. For instance, in
Figure \ref{fig:intersection-record} two types are defined
\nickel{Animal} and \nickel{Pet}, and a variable that is compatible
with both types is declared, with type \nickel{Animal @& Pet}. This
particular application is supported, for instance, by TypeScript.

@@

Once again, intersection contracts introduce side-effects in the picture. What's
more, these side-effects interact with user-defined contracts in a non-trivial
way, while they are an important feature for validation.
\unsure{(Yann) Should we talk about thiemann here, who do support user-defined
contracts?}
% But this should not have happened, since in the program of Figure
% \ref{fig:inter-flat-contracts} \nickel{g} is never applied to \nickel{0}, in
% fact, it is never applied to anything.  Checking if \nickel{C} has already
% failed, and marking \nickel{Str -> Str} as failed negatively on \nickel{l}
% is not enough, the contract \nickel{Str -> Str} should not have been used
% inside the evaluation of \nickel{C}, which adds an extra layer of complexity:
% contracts should be guarded, and execution depends on the shape of the
% surrounding evaluation context.

\subsection{Challenging the semantics}

@@

% Curiously, union and intersection type systems, on which
% \cite{KeilThiemannUnionIntersection} are basing their semantics on, don't
% exhibit this property. Subtyping allows to correctly type check a term like
% \nickel{g 1} as both \nickel{Num -> Num} as well as
% \nickel{Bool -> Num}, and then deducing that \nickel{g 1}
% can be given the type \nickel{Num -> Num @& Bool -> Num}.
\resolved{(Yann) I just reworked the wording, but I'm not totally sold on the
argument
(Teo) I agree, I think it would need to be expanded for it to actually
say something, I'll remove it}

\subsection{Keil and Thiemann}
\label{sec:keil-thiemann}
\unsure{Subsection title?}

@@

\subsection{Williams, Morris, and Wadler}
\label{sec:will-morr-wadl}
\unsure{Subsection title?}

@@

>>>>

Yet, intersections are useful in their own right. They can be used to
combine dictionaries in the style of object-oriented multiple inheritance. For instance, in
Figure \ref{fig:intersection-record} two types are defined
\nickel{Animal} and \nickel{Pet}, and a variable that is compatible
with both types is declared, with type \nickel{Animal @& Pet}. This
particular application is supported, for instance, by TypeScript.

@@

Once again, intersection contracts introduce side-effects in the picture. What's
more, these side-effects interact with user-defined contracts in a non-trivial
way, while they are an important feature for validation.
\unsure{(Yann) Should we talk about thiemann here, who do support user-defined
contracts?}

\subsection{A semantics based on types}

@@

\subsection{A first realization}
\label{sec:keil-thiemann}
\unsure{Subsection title?}

@@

\subsection{Monitoring properties}
\label{sec:will-morr-wadl}
\unsure{Subsection title?}

@@

% Local Variables:
% ispell-dictionary: "american"
% End:
